|

### 2020-09-18 paper.Rmd
Some changes to the discussion.

In this paper we have introduced the sage display, as a visualisation technique for reversing
the curse of dimensionality in high dimensional projections, and have shown its utility in applications in the natural sciences and machine learning. Our case studies highlight that the radial transformation can reduce the effects of data piling, and in combination with the grand tour our new sage display provides interpretable visualisation, while preserving global structure in high dimensional space.

@@

For the sage display tuning is often required to avoid bunching points in the 
visualisation, especially if the projection is dense in the center of the 
distribution. Expanding around the center aggressively can introduce distortions
in the display, a well known problem for other NLDR methods as well.
However, unlike those methods, the parameters in the sage display are 
interpretable; we know the effect of altering $\gamma$ and $R$ on the resulting 
visualisation. Our parameter tuning example highlights this: the sage display is 
linear up to a  given effective dimension; the default sage display, preserves 
the correlation between the variables which is broken once points get moved
to the edge of the hypersphere as $\gamma$ and $R$ are changed. Given
that the display is quick to compute, being able to modify these parameters in 
real time with an interactive interface would be beneficial.  Currently, the 
sage display is naive to information in high dimensional space that is not 
captured by linear projections. Like t-SNE, it would be interesting to explore
transformations of projections where points in the high dimensional space are 
locally dense instead of expanding from the center of the distribution.

>>>>

In this paper we have introduced the sage display, a visualisation technique for reversing
the curse of dimensionality in low dimensional projections of high dimensional data, and have shown its utility in applications in the natural sciences and machine learning. Our case studies highlight that the radial transformation can reduce the effects of data piling, and in combination with the grand tour our new sage display provides interpretable visualisation, while preserving global structure in high dimensional space.

The applications also highlight that tuning is often required,
especially if the projection is dense in the center of the 
distribution. Expanding around the center aggressively can introduce distortions
in the display, a well known problem for other NLDR methods as well.
However, unlike those methods, the parameters in the sage display are 
interpretable; we know the effect of altering $\gamma$ and $R$ on the resulting 
visualisation. Recall that the radial transformation is approximately linear near
the center, thus preserving structures such as those seen in the pdfsense and
pollen applications. On the other hand, the tuning example showed how points away
from the projected center get moved to the edge of the hypersphere as $\gamma$
is increased or $R$ is decreased. 
<!--
Our parameter tuning example highlights this: the sage display is 
linear up to a  given effective dimension; the default sage display, preserves 
the correlation between the variables which is broken once points get moved
to the edge of the hypersphere as $\gamma$ and $R$ are changed.
-->
Given
that the display is quick to compute, being able to modify these parameters in 
real time with an interactive interface would be beneficial.

Currently, the 
sage display is naive to information in high dimensional space that is not 
captured by linear projections. Like t-SNE, it would be interesting to explore
transformations of projections where points in the high dimensional space are 
locally dense instead of expanding from the center of the distribution.

@@
